%-------------------------------------------------------------------------------
% SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}

%-------------------------------------------------------------------------------
% CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

\cventry%
 {Data Engineer}
 {Ontario Public Service --- Ministry of the Attorney General}
 {Toronto, Canada}
 {2024 --- Present}
 {
	\begin{cvitems}
		\item Driving technology modernization initiative for sensitive judicial data processing, serving as key technical contributor, change advocate, and stakeholder coordinator for modern analytics approaches across Ontario's court system during ongoing 7-year system migration worth \$160M+.
		\item Delivered \$300K annual cost savings by implementing modern data transformation platform (DBT), eliminating legacy IBM Cognos licensing across 4 teams while maintaining service delivery during transition.
		\item Coordinating cross-functional technology delivery across IT operations, analytics teams, and legacy mainframe specialists, ensuring alignment with executive reporting requirements and public accountability measures.
		\item Designed data warehouse supporting reporting across 150+ provincial courts, enabling executive and public reporting on case flow that directly informs multi-million dollar investments in court locations, judicial staffing, and child welfare services.
		\item Conducted comprehensive security and privacy auditing of data processing tools, ensuring compliance with RCMP security requirements and judicial data protection standards.
		\item Implementing agile methodologies and coordinating deliverables across multiple teams, ensuring timeline adherence during complex data migration while maintaining operational continuity for critical court operations.
	\end{cvitems}
 }

 \cventry%
 {Senior Research Analyst/Team Lead}
 {Ontario Public Service --- Treasury Board Secretariat}
 {Toronto, Canada}
 {2019 --- 2024}
 {
	\begin{cvitems}
        \item Led cross-ministry technology evaluation for multi-million dollar government initiatives through Strategic Planning Process (SPP), providing analytical assessment and strategic recommendations for funding decisions across multiple ministries.
        \item Managed the procurement, implementation, and delivery pipeline for automation platform informing union negotiation teams involving 60,000+ employees worth hundreds of millions, coordinating across ministries and executive leadership.
        \item Delivered \$120K+ in cost savings through strategic analysis and adoption of open source technologies and modern development practices, while maintaining operational excellence and service delivery.
        \item Led a cross-functional team of 5 through technology implementation and delivery, providing performance feedback, professional development, and technical guidance on modern development practices and infrastructure optimization.
        \item Evaluated and managed technology procurement processes, leveraging open source solutions and cloud integration to implement cost-effective data loading and processing solutions.
        \item Implemented CI/CD practices and agile methodologies in team environment, managing version control workflows and establishing quality assurance processes to ensure reliable solution delivery.
    \end{cvitems}
 }

\cventry%
	{Workforce Analyst}
	{Ontario Public Service --- Ministry of Government \& Consumer Services}
	{Toronto, Canada}
	{2017 --- 2019}
	{
		\begin{cvitems}
			\item Coordinated delivery of province-wide job reclassification project affecting 10,000+ employees, automating generation of 7,000+ executive-level reclassification packages and ensuring timely delivery across multiple ministries within union-negotiated deadlines.
			\item Managed data flow of classification work, union representatives, and ministry executives, ensuring accurate delivery of salary, duty, and title changes during critical organizational transformation.
			\item Delivered significant process improvements through automated job description comparison tools, reducing manual classification work by 70+ hours while improving accuracy and consistency across government positions.
			\item Implemented data quality assurance processes across multiple systems, establishing standards and protocols that improved data reliability and reduced errors in workforce reporting and analysis.
		\end{cvitems}
	}

	\cvcompactentry%
	{Linux System Administrator}
	{Soho VFX}
	{Toronto, Canada}
	{2016 --- 2017}
	{}
\end{cventries}