\storeletterdate{\today}
\storerecipient{Waterloo Regional Health Network}{Human Resources Department}
\storelettertitle{Job Application for Senior Data Engineer (Job ID: 5629)}
\storeletteropening{Dear Hiring Manager,}

\begin{storedcvletter}{
I am writing to express my strong interest in the Senior Data Engineer position at Waterloo Regional Health Network. As someone who has personally experienced the exceptional care at Grand River Hospital as a patient, I am excited about the opportunity to contribute to WRHN's mission of improving lives and building healthier communities through data-driven healthcare solutions.

With over seven years of experience building scalable data infrastructure in highly regulated government environments, I bring directly transferable expertise in managing sensitive data while maintaining strict compliance standards. My current role at Ontario's Ministry of the Attorney General has equipped me with deep experience in data governance, privacy protection, and regulatory compliance—skills that align perfectly with PHIPA requirements and healthcare data security standards.

At the Ministry of the Attorney General, I have saved over \$300,000 annually by implementing modern data pipelines that integrate multiple legacy systems into unified platforms.\@ This experience directly parallels the challenge of integrating complex systems at WRHN.\@ I have successfully managed critical data migrations across Ontario's entire court system with RCMP security clearance, ensuring seamless data flow while maintaining the highest security standards—experience that translates directly to handling sensitive patient data.

My technical expertise spans the exact technologies outlined in your requirements: SQL Server, Oracle, Python, Azure cloud platforms, and ETL pipeline development. I also have familiarity with healthcare data standards such as FHIR, and my privacy-focused approach demonstrates my commitment to data protection principles essential in healthcare environments. In my previous role at Treasury Board Secretariat, I led a team of five engineers, mentoring junior staff through complex technical challenges while delivering enterprise solutions that supported multi-million dollar government decisions.

While my background is in government rather than healthcare, I am passionate about leveraging data to help people and have several personal projects related to healthcare applications. The opportunity to work with clinical and operational data that directly impacts patient outcomes represents exactly the kind of meaningful work I want to pursue. I am excited about contributing to WRHN's innovative approach to healthcare delivery.

I would welcome the opportunity to discuss how my experience with sensitive data management, cross-functional team leadership, and scalable data infrastructure can contribute to WRHN's mission of connecting communities to the right care at the right time.
}
\end{storedcvletter}

\storeletterclosing{Sincerely,}
\storeletterenclosure[Attached]{Resume}