%-------------------------------------------------------------------------------
% SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}

%-------------------------------------------------------------------------------
% CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

\cventry%
 {Data Engineer}
 {Ontario Public Service --- Ministry of the Attorney General}
 {Toronto, Canada}
 {2024 --- Present}
 {
	\begin{cvitems}
		\item Saved over \$300K annually by implementing DBT for unified court data model, modernizing legacy mainframe systems while ensuring regulatory compliance throughout critical 7-year system migration.
		\item Managed sensitive judicial data with RCMP security clearance, maintaining strict data governance and privacy protection across Ontario's entire court system.
		\item Designed scalable data warehouse supporting analytical reporting covering 150+ provincial courts that drives multi-million dollar decisions on court operations and resource allocation.
		\item Built and maintained Azure cloud infrastructure with Databricks and Data Factory, integrating multiple legacy systems into unified platform for seamless data flow and analytics.
		\item Developed DBT transformations converting complex data models for large-scale processing, ensuring data quality and accessibility for critical business operations.
		\item Led cross-functional collaboration across multiple teams during \$160M+ system migration, implementing agile methodologies to ensure project timeline success.
	\end{cvitems}
 }

 \cventry%
 {Data Engineer/Team Lead}
 {Ontario Public Service --- Treasury Board Secretariat}
 {Toronto, Canada}
 {2019 --- 2024}
 {
    \begin{cvitems}
        \item Led team of 5 engineers delivering enterprise data solutions for executive decision-making, mentoring junior staff through complex technical challenges and code optimization.
        \item Automated critical data pipelines supporting multi-million dollar union negotiations, transforming manual processes into real-time dashboards for government leadership.
        \item Architected scalable Azure cloud infrastructure and implemented CI/CD practices, ensuring reliable system performance and efficient development workflows.
        \item Established data governance standards and quality processes, conducting regular code reviews and providing technical guidance on data modeling and integration best practices.
        \item Developed entity resolution tools and advanced analytics using Python, improving data accuracy and enabling junior staff to validate complex data models effectively.
    \end{cvitems}
 }

\cventry%
	{Workforce Analyst}
	{Ontario Public Service --- Ministry of Government \& Consumer Services}
	{Toronto, Canada}
	{2017 --- 2019}
	{
		\begin{cvitems}
			\item Automated generation of 7,000+ executive packages for province-wide project affecting 10,000 employees, eliminating manual processes while ensuring data accuracy and regulatory compliance.
			\item Built scalable data pipelines and quality validation tools, reducing operational overhead by 70+ hours while maintaining high standards for critical government operations.
			\item Ensured data integrity across multiple legacy systems through systematic quality checks and process improvements.
		\end{cvitems}
	}

\end{cventries}