%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

% \cventry
%   {Owner/Operator}
%   {TWDickson Consulting}
%   {Toronto, Canada}
%   {October 20, 2021 - Present}
%   {
%     \begin{cvitems}
%       \item Providing web development, automation, and data engineering expertise.
%       \item Designing and coding a static site generator for \textbf{Topology Health} (https://topology.health).
%       \item Working closely with clients to produce a uniform and harmonized information architecture.
%       \item Creating documentation for knowledge transfer, facilitating easy client site maintenance.
%       \item Implementing robust content management systems for seamless website updates.
%       \item Successfully managing client relationships through various remote communication platforms.
%     \end{cvitems}
%   }

\cventry%
 {Data Engineer}
 {Ontario Public Service --- Attorney General}
 {Toronto, Canada}
 {2024 --- Present}
 {
  \begin{cvitems}
  \item Working in a high security environment with sensitive data, ensuring compliance with data protection standards
  \item Led the implementation of Data Build Tool (DBT) for data transformation and modelling, enhancing data quality and consistency across multiple data sources
  \item Designed and implemented dimensional model of data warehouse using Kimball methodology, improving data accessibility and reporting capabilities
  \item Collaborated with cross-functional teams to define data requirements, ensuring alignment with business objectives and enhancing data-driven decision-making processes
  \item Managed performance tuning and optimization of existing ETL processes, resulting in improved data processing times and reduced resource consumption
  \item Developed comprehensive documentation for data models, ETL processes, and system architecture to facilitate knowledge transfer and ensure maintainability of solutions
  \item Created and maintained project gantt charts and timelines, coordinating tasks and deliverables to ensure meeting production deadlines
  \end{cvitems}
 }

\cventry%
  {Data Engineer/Team Lead}
  {Ontario Public Service --- Treasury Board Secretariat}
  {Toronto, Canada}
  {2019 --- 2024}
  {
    \begin{cvitems}
      \item Led the division's data overhaul project, modernizing and enhancing digital data infrastructure. Utilized Python and Pandas for local data processing, uploading data from Excel inputs to an Azure cloud database using SQLAlchemy, and building robust data models to support advanced analytics.
      \item Directed a team of 5 in data pipeline development, orchestrating ETL processes, data warehousing solutions, and real-time data streaming to improve data accessibility and analytics capabilities.
      \item Managed the procurement and implementation of advanced data engineering tools and technologies, including Azure Data Factory, Azure SQL Server, and Azure PowerApps, leading to over \$100k in cost savings.
      \item Suggested and implemented tools such as GitHub for version control and CMSs for content management, improving collaboration and workflow efficiency.
      \item Supervised the hiring, onboarding, and mentorship of co-op students and new staff, assigned tasks, managed pull requests, git repositories, and branches, fostering a collaborative and productive team environment.
      \item Conducted regular team meetings, acted as a manager, and provided leadership in project planning and execution, ensuring alignment with organizational goals.
      \item Coordinated with cross-functional teams to design robust software architectures, define technical requirements, and ensure seamless integration of data engineering solutions across various platforms.
      \item Conducted regular code reviews, provided technical guidance on data modelling, data integration, and pipeline optimization, promoting high-quality and maintainable code.
      \item Developed internal data cleaning and transformation tools using RESTful API design with Flask/Django/Node, and Vue.js, connected to an Azure database, enhancing data quality and consistency.
      \item Tackled significant challenges in name entity recognition using Levenshtein distances and the NLTK library in Python, improving data accuracy and processing efficiency.
    \end{cvitems}
  }

\cventry%
  {Workforce Analyst}
  {Ontario Public Service --- Ministry of Government \& Consumer Services}
  {Toronto, Canada}
  {2017 --- 2019}
  {
    \begin{cvitems}
      \item Utilized SQL, MS Access, Excel, VBA, and Python for data management, reporting, visualization, and process automation, supporting business operations with timely and accurate data insights.
      \item Automated the generation and distribution of over 7000 customized documents, significantly reducing manual labor and enabling directors to quickly access and analyze their staff information.
      \item Created and optimized reports comparing content across multiple documents, improving efficiency and accuracy in data reporting and reducing manual workload.
      \item Ensured data integrity across multiple systems through regular data quality checks and recommended enhancements to data management processes to improve overall data reliability.
      %S\item Collaborated with cross-functional teams to analyze workforce trends, identify improvement areas, and develop an equitable job classification system, contributing to more informed decision-making.
    \end{cvitems}
  }

\cventry%
  {Linux System Administrator}
  {Soho VFX}
  {Toronto, Canada}
  {2016 --- 2017}
  {
    \begin{cvitems}
      \item Upgraded the render farm by setting up, installing, and configuring new servers, resulting in improved performance and reduced rendering times for large-scale visual effects projects.
      \item Automated repetitive tasks, upgraded software, and optimized systems to provide efficient technical support, saving significant time and ensuring high system performance.
      \item Recognized for outstanding contributions as a Systems Administrator in the production of the movie Logan (2017).
      \item Performed routine maintenance and troubleshooting of hardware and software, ensuring smooth operation and minimal downtime, which was crucial for meeting production deadlines.
    \end{cvitems}
  }
\end{cventries}
