%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

% \cventry
%   {Owner/Operator}
%   {TWDickson Consulting}
%   {Toronto, Canada}
%   {October 20, 2021 - Present}
%   {
%     \begin{cvitems}
%       \item Providing web development, automation, and data engineering expertise.
%       \item Designing and coding a static site generator for \textbf{Topology Health} (https://topology.health).
%       \item Working closely with clients to produce a uniform and harmonized information architecture.
%       \item Creating documentation for knowledge transfer, facilitating easy client site maintenance.
%       \item Implementing robust content management systems for seamless website updates.
%       \item Successfully managing client relationships through various remote communication platforms.
%     \end{cvitems}
%   }

\documentclass{article}
\usepackage{etoolbox}

% Define the version here
\newcommand{\oversion}{dev-ops} % Change to "data-engineer", "dev-ops", or "default"

\begin{document}

% Title based on \oversion
\ifstrequal{\oversion}{data-engineer}{%
  \title{Resume - Data Engineer Version}%
}{%
\ifstrequal{\oversion}{dev-ops}{%
  \title{Resume - Dev Ops Version}%
}{%
  \title{Resume - Default Version}%
}}

\maketitle

\section{Experience}

\cventry
  {Senior Research Analyst/Team Lead}
  {Ontario Public Service - Treasury Board Secretariat}
  {Toronto, Canada}
  {2019 - Present}
  {
    \begin{cvitems}
      \item Led the division's data overhaul project, modernizing and enhancing digital data infrastructure, including partial migration to Azure cloud and Google Apps Scripts for automated processes.
      \item Managed a team of 5, implementing CI/CD pipelines using GitHub Actions in personal projects, automating build and deployment processes, demonstrating capability to adopt similar practices in professional settings.
      \item Procured and integrated key tools such as GitHub for version control, improving collaboration and code management across the team.
      \item Automated infrastructure provisioning and application deployments using Docker and Docker-Compose, managing containers and storage to ensure consistent and efficient operations.
      \item Conducted regular code reviews, managed Git repositories, and implemented branching strategies and merge request processes to ensure code quality and collaboration within the team.
      \item Developed scripts in Python and BASH to automate routine tasks, improve operational efficiency, and manage server resources, demonstrating strong scripting and automation skills.
      \item Provided mentorship and guidance to team members on best practices in DevOps, cloud infrastructure management, and automation techniques, fostering a culture of continuous improvement and learning.
    \end{cvitems}
  }

\cventry
  {Workforce Analyst}
  {Ontario Public Service - Ministry of Government \& Consumer Services}
  {Toronto, Canada}
  {2017 - 2019}
  {
    \begin{cvitems}
      \item Leveraged data management and automation skills using SQL, Python, and VBA to support business operations, significantly improving data processing and reporting capabilities.
      \item Automated the generation and distribution of over 7000 customized documents, reducing manual labor and enabling faster access to critical information for decision-makers.
      \item Implemented data quality checks and recommended improvements to data management processes, ensuring data integrity across multiple systems and reducing errors.
      \item Collaborated with cross-functional teams to analyze workforce trends and develop data-driven insights for strategic planning and resource allocation.
    \end{cvitems}
  }

\cventry
  {Junior System Administrator}
  {Soho VFX}
  {Toronto, Canada}
  {2016 - 2017}
  {
    \begin{cvitems}
      \item Completed a render farm upgrade by setting up, installing, and configuring new servers, resulting in improved performance and reduced rendering times.
      \item Automated repetitive tasks and optimized systems using BASH scripting, contributing to ongoing operational efficiencies and time savings.
      \item Provided technical support and performed routine maintenance and troubleshooting of hardware and software, ensuring minimal downtime and smooth operation of systems.
      \item Participated in incident management and on-call rotations, handling system reliability and ensuring quick resolution of issues.
    \end{cvitems}
  }


\end{cventries}
