%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

\cventry
  {Senior Research Analyst/Team Lead}
  {Ontario Public Service - Treasury Board Secretariat}
  {Toronto, Canada}
  {2019 - Present}
  {
    \begin{cvitems}
      \item Led the division's data overhaul project to modernize and enhance digital data infrastructure, including migration to Azure cloud using Python and Pandas for improved efficiency and AI readiness.
      \item Designed and developed internal data cleaning tools using Flask, Django, Node.js (Express) for the backend and Vue.js, HTML, CSS, and JavaScript for the frontend, integrating with Azure databases and RESTful APIs.
      \item Implemented efficient pagination algorithms using offset for APIs that allowed users to clean and merge records, ensuring robust and scalable backend processes.
      \item Managed a team of 5, conducting regular code reviews, providing guidance on software design principles, and ensuring adherence to coding standards.
      \item Coordinated project planning and scheduling, collaborating with cross-functional teams to define technical requirements and software architecture for new applications.
      \item Assisted with software procurement and guided divisional roadmaps for future digital service expansion, resulting in cost savings of over \$100k.
      \item Oversaw co-op student hiring, onboarding, and project assignments related to automation, AI research, and infrastructure upgrades, fostering team growth and development.
    \end{cvitems}
  }

\cventry
  {Workforce Analyst}
  {Ontario Public Service - Ministry of Government \& Consumer Services}
  {Toronto, Canada}
  {2017 - 2019}
  {
    \begin{cvitems}
      \item Developed automated solutions for data management, reporting, and visualization using SQL, MS Access, Excel, VBA, and Python, significantly improving business operations efficiency.
      \item Automated the generation and distribution of over 7000 customized documents, reducing manual labor by a month and enabling quick access to reporting staff information for directors.
      \item Created new reports to compare content across multiple Word documents, optimizing the process to improve data accuracy and reduce manual work.
      \item Maintained data integrity across multiple systems, performing regular data quality checks and recommending improvements to data management processes.
      \item Collaborated with cross-functional teams to analyze workforce trends, identify areas for improvement, and develop an equitable job classification system.
    \end{cvitems}
  }

\cventry
  {Junior System Administrator}
  {Soho VFX}
  {Toronto, Canada}
  {2016 - 2017}
  {
    \begin{cvitems}
      \item Upgraded the render farm by setting up, installing, and configuring new servers, resulting in improved performance and reduced rendering times.
      \item Automated repetitive tasks, upgraded software, and optimized systems, leading to ongoing savings of one hour per week for technical support staff.
      \item Provided technical support to employees, ensuring smooth operation of systems and minimizing downtime through routine maintenance and troubleshooting of hardware and software.
    \end{cvitems}
  }

\cventry
  {Owner/Operator}
  {TWDickson Consulting}
  {Toronto, Canada}
  {2021 - Present}
  {
    \begin{cvitems}
      \item Providing web development, automation, and data engineering expertise.
      \item Built and implemented websites using GoLang CMS systems like Hugo, delivering high-performance, static websites for various clients such as \textbf{Topology Health} (https://topology.health).
      \item Worked closely with clients to produce a uniform and harmonized information architecture.
      \item Created documentation for knowledge transfer, facilitating easy client site maintenance.
      \item Employed Agile and Waterfall methodologies, adapting to client requirements and project scopes to deliver efficient and timely solutions.
      \item Successfully managed client relationships through various remote communication platforms.
    \end{cvitems}
  }
\end{cventries}
