%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

% \cventry
%   {Owner/Operator}
%   {TWDickson Consulting}
%   {Toronto, Canada}
%   {October 20, 2021 - Present}
%   {
%     \begin{cvitems}
%       \item Providing web development, automation, and data engineering expertise.
%       \item Designing and coding a static site generator for \textbf{Topology Health} (https://topology.health).
%       \item Working closely with clients to produce a uniform and harmonized information architecture.
%       \item Creating documentation for knowledge transfer, facilitating easy client site maintenance.
%       \item Implementing robust content management systems for seamless website updates.
%       \item Successfully managing client relationships through various remote communication platforms.
%     \end{cvitems}
%   }

\cventry
  {Senior Research Analyst/Team Lead}
  {Ontario Public Service - Treasury Board Secretariat}
  {Toronto, Canada}
  {2019 - Present}
  {
    \begin{cvitems}
      \item Leading the division's data overhaul project to modernize and enhance digital data infrastructure, including migration to Azure cloud using Python and Pandas for improved efficiency and AI readiness.
      \item Managed a team of 5, held regular team meetings, assigned tasks and duties, followed up with team members, and coordinated with senior management. 
      \item  Assisted with software procurement and guiding divisional roadmaps for future digital service expansion, resulting in significant cost savings of over \$100k.
      \item Overseeing co-op student hiring, onboarding, and assigning projects and tasks relating to automation, AI research, and infrastructure upgrades, contributing to the team's growth and development.
      \item Coordinating project planning and scheduling; designing software architecture and collaborating with cross-functional teams to define technical requirements and specifications for software development.
      \item Conducting regular code reviews and providing guidance on software design principles and coding standards, promoting consistency and quality across the team's codebase.
    \end{cvitems}
  }

\cventry
  {Workforce Analyst}
  {Ontario Public Service - Ministry of Government \& Consumer Services}
  {Toronto, Canada}
  {2017 - 2019}
  {
    \begin{cvitems}
      \item Leveraged expertise in data management, reporting, visualization, and process automation using tools such as SQL, MS Access, Excel, VBA, and Python to support business operations.
      \item Automated the generation and distribution of over 7000 customized documents, reducing manual labour by a month and enabling directors to quickly view their reporting staff information through customized summary documents.
      \item Developed new reports that compare content across multiple Word documents, optimizing reports to run more efficiently with less manual work and improving data accuracy.
      \item Maintained and improving data integrity across multiple systems, performing regular data quality checks and recommending improvements to data management processes.
      \item Collaborated with cross-functional teams to analyze workforce trends, identify areas of improvement, and develop an equitable job classification system.
    \end{cvitems}
  }

\cventry
  {Junior System Administrator}
  {Soho VFX}
  {Toronto, Canada}
  {2016 - 2017}
  {
    \begin{cvitems}
      \item Completed a render farm upgrade by setting up, installing, and configuring new servers, resulting in improved performance and reduced rendering times.
      \item Provided technical support to employees by automating repetitive tasks, upgrading software, and optimizing systems, resulting in an ongoing savings of one hour per week.
      \item Recognized for contributions as a Systems Administrator in Logan (2017).
      \item Conducted routine maintenance and troubleshooting of hardware and software, ensuring the smooth operation of systems and minimizing downtime.
    \end{cvitems}
  }

\end{cventries}
