\storeletterdate{\today}
\storerecipient{Procurify}{Engineering Team}
\storelettertitle{Application for Senior Backend Engineer, Platform \& Integrations}
\storeletteropening{Dear Procurify Hiring Team,}

\begin{storedcvletter}{
I am excited to apply for the Senior Backend Engineer position on your Platform \& Integrations team. With 7+ years of experience building scalable APIs and integration platforms for critical government systems, I'm drawn to Procurify's mission to modernize spend management through robust, API-first architecture. Your focus on creating seamless connections to accounting and ERP systems aligns perfectly with my expertise in building resilient data pipelines and third-party integrations.

In my current role as a Data Engineer with a Platform and Integration focus at the Ontario Public Service, I've developed the exact capabilities you're seeking. I recently architected and implemented a Python-based data platform that eliminated over \$300K in annual licensing costs while processing millions of rows of critical court data. This experience translates directly to your need for scalable, observable systems capable of handling high-volume data from thousands of customers.

My hands-on experience with Flask and RESTful API design matches your technical requirements well. I've built API-based data cleaning tools that transformed weeks of manual processing into automated workflows—the kind of seamless integration experience that drives customer satisfaction. While my cloud experience has been primarily with Azure, the core principles of containerization (Docker), CI/CD pipelines, and infrastructure as code (Terraform) apply directly to your AWS environment.

Third-party API integrations have been central to my work. I've successfully integrated multiple data sources through Python and SQL, creating automated document generation systems that process 7,000+ customized reports. I've also eliminated high-risk legacy systems by building modern, maintainable replacements—experience that will be valuable as you expand your ecosystem of accounting and ERP integrations. My work with entity resolution algorithms and data transformations has given me a solid understanding of the challenges that arise when connecting disparate systems.

From an architectural perspective, I focus on making pragmatic decisions that balance immediate needs with long-term scalability. I've implemented protected main branches with automated testing, designed data warehouses supporting reporting across Ontario's entire court system, and consistently built the infrastructure that keeps complex organizations running smoothly. This approach ensures systems remain maintainable and scalable as they evolve.

As a team lead, I've mentored 5 engineers through complex technical challenges while maintaining delivery standards during organizational changes. I believe strongly in thorough code reviews, collaborative design sessions, and fostering engineering excellence. My goal is always to help elevate the capabilities of the entire team through knowledge sharing and practical guidance.

Procurify's recent Series C funding and commitment to AI-enhanced procure-to-pay experiences represents an exciting growth opportunity. Your remote-first culture and focus on personal development resonate with me, and I'm particularly interested in your API-first strategy and the opportunity to work with modern frameworks like FastAPI at scale. Building integrations that directly impact how organizations manage their spending is exactly the type of meaningful technical challenge I seek.

I would welcome the opportunity to bring my expertise in building resilient backend services and scalable integrations to help Procurify strengthen its position as a leader in modern spend management. Thank you for considering my application. I look forward to discussing how my experience eliminating costly legacy systems and building modern API platforms can contribute to your Platform team's success.
}
\end{storedcvletter}

\storeletterclosing{Best regards,}
\storeletterenclosure[Attached]{Resume}