\storeletterdate{\today}
\storerecipient{Poka}{Analytics Team}
\storelettertitle{Application for Senior Data Developer Position}
\storeletteropening{Dear Hiring Manager,}

\begin{storedcvletter}{
I am writing to express my strong interest in the Senior Data Developer position at Poka. Your mission to bridge the gap between frontline workers and smart factory technology particularly resonates with me. After building data solutions that support critical government operations for seven years, I am drawn to the opportunity to create direct, measurable impact in manufacturing environments where data insights drive tangible improvements.

My experience aligns closely with your technical requirements. At the Ministry of the Attorney General, I architected and optimized DBT pipelines that achieved over \$300K in annual cost savings through strategic implementation of incremental builds and performance profiling. Managing data from 150+ court locations with stringent compliance requirements has prepared me well for the complexity and scale of manufacturing data environments. This work required not just technical expertise, but a deep understanding of how to build reliable, scalable systems that stakeholders can trust for critical decisions.

Your technology stack aligns well with my expertise. I have extensive experience building dimensional models using Star and Snowflake schemas, developing Flask APIs for data processing and entity resolution, and implementing Azure cloud infrastructure including Databricks and Data Factory. Beyond the technical implementation, I have consistently applied software engineering best practices—establishing CI/CD pipelines, automated testing frameworks, and rigorous code review processes. This foundation ensures that data solutions are not just functional, but maintainable and scalable as organizational needs evolve.

In my role at Treasury Board Secretariat, I led a team of five engineers in developing enterprise data solutions that supported multi-million dollar government spending decisions. This experience taught me to effectively translate complex business requirements into robust technical solutions while managing diverse stakeholder expectations and project timelines. I understand the importance of clear communication across technical and non-technical teams—a skill that would be valuable when collaborating with your product managers and cross-functional teams.

While my background is in government data systems, I recognize strong parallels with manufacturing challenges: integrating heterogeneous data sources, ensuring real-time data quality, optimizing performance under constraints, and delivering actionable insights for operational decisions. The opportunity to apply these skills to near real-time manufacturing pipelines represents an exciting technical challenge. Additionally, I am eager to expand my work with AI-driven use cases, building on my experience with entity resolution algorithms to explore advanced analytics applications in your platform.

The mentoring component of this role particularly appeals to me. Throughout my career, I have found great satisfaction in guiding junior engineers, sharing technical knowledge, and helping teams adopt best practices. This collaborative approach to growth aligns with my belief that strong teams are built through knowledge sharing and continuous learning.

I am confident that my combination of technical expertise in data engineering, proven ability to deliver measurable business value, and experience leading cross-functional teams would make me a valuable addition to Poka's Analytics team. I would welcome the opportunity to discuss how my skills and experience can contribute to advancing your data platform and supporting your mission of empowering frontline manufacturing workers.
}
\end{storedcvletter}

\storeletterclosing{Sincerely,}
\storeletterenclosure[Attached]{Resume}