\cvsection{Experience}
\begin{cventries}

\cventry%
	{Data Engineer}
	{Ontario Public Service --- Ministry of the Attorney General}
	{Toronto, Canada}
	{2024 --- Present}
	{
		\begin{cvitems}
			\item Saved over \$300K annually by optimizing DBT pipeline performance through profiling and incremental build migration, improving data processing efficiency and reducing compute costs for large-scale analytics.
			\item Designed dimensional data models using Kimball methodology (Star/Snowflake schema), ensuring data accessibility and analytical reporting capabilities for 150+ provincial courts.
			\item Built and maintained Azure cloud infrastructure with Databricks and Data Factory, integrating multiple legacy systems into unified platform for seamless data flow and analytics.
			\item Led cross-functional collaboration across multiple teams during \$160M+ system migration, implementing agile methodologies to ensure project timeline success.
			\item Developed DBT transformations with SQL optimization for large-scale data processing with strict governance and regulatory compliance throughout critical 7-year system modernization.\item Designed scalable data warehouse supporting analytical reporting that drives multi-million dollar decisions on operations and resource allocation.
		\end{cvitems}
	}

\cventry%
	{Data Engineer/Team Lead}
	{Ontario Public Service --- Treasury Board Secretariat}
	{Toronto, Canada}
	{2019 --- 2024}
	{
		\begin{cvitems}
			\item Developed production Flask APIs for internal data cleaning applications, enabling team collaboration through web-based interfaces for entity resolution and data verification workflows.
			\item Led team of 5 engineers delivering enterprise data solutions for executive decision-making, mentoring junior staff through complex technical challenges and code optimization.
			\item Implemented entity resolution algorithms using Python and NLTK for complex name matching, improving data accuracy across multiple data sources with RESTful API design.
			\item Architected scalable Azure cloud infrastructure and implemented CI/CD practices, ensuring reliable system performance and efficient development workflows.
			\item Automated critical data pipelines supporting multi-million dollar decisions, transforming manual processes into real-time dashboards with established automated testing and code review standards.
			\item Established data governance and quality processes, providing technical guidance on data modeling best practices and advanced analytics development.
		\end{cvitems}
	}

\cventry%
	{Workforce Analyst}
	{Ontario Public Service --- Ministry of Government \& Consumer Services}
	{Toronto, Canada}
	{2017 --- 2019}
	{
		\begin{cvitems}
			\item Automated generation of 7,000+ executive packages for province-wide project affecting 10,000 employees, eliminating manual processes while ensuring data accuracy and regulatory compliance.
			\item Built scalable data pipelines and quality validation tools, reducing operational overhead by 70+ hours while maintaining high standards for critical operations.
		\end{cvitems}
	}

\end{cventries}